\documentclass[11pt]{article}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\setmainfont{Bodoni 72 Book}
\usepackage[paperwidth=8.5in,paperheight=11in,margin=1in,headheight=0.0in,footskip=0.5in,includehead,includefoot,portrait]{geometry}
\usepackage[absolute]{textpos}
\TPGrid[0.5in, 0.25in]{23}{24}
\parindent=0pt
\parskip=12pt
\usepackage{nopageno}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{amsmath}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}

\begin{document}

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\huge Biography
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Trinton (*2000) was born in Georgia and grew up in Alabama (2000-2011), and Georgia (2011-2019). They are a technologist, performer (reader, vocalist, percussionist, synthesist), poet, and composer of acoustic and electroacoustic concert music. Their concerns as an artist include experiences of non-semantic knowledge, the power and agency of symbols, and the effects of accumulated understanding on human perception. Trinton's work has been performed throughout the United States and in Austria. \\ Trinton's music has been performed by soloists and ensembles such as Irvine Arditti (Vienna, Austria), the JACK Quartet, (Iowa City, Iowa),  Ensemble Dal Niente (Iowa City, Iowa), Ensemble PHACE (Vienna, Austria), the University of Iowa Center for New Music Ensemble (Iowa City, Iowa), and the Eastman Graduate Composers' Sinfonietta (Rochester, New York). Trinton has performed and had music performed at festivals such as the Midwest Composers' Symposium (Bloomington, Indiana), the Summer Institute for Contemporary Performance Practice (Boston, Massachusetts), and the Vienna Summer Music Festival (Vienna, Austria). \\ Trinton has served as an instructor of undergraduate music theory and digital art at the University of Iowa, and as an instructor of electronic music at the Eastman School of Music. They have worked as a composer and music director of music theatre (Staunton, Virginia), a theater technician (Brevard, North Carolina), a percussionist and pianist in independent and blues ensembles (Atlanta, Georgia; Rochester, New York), and as a media technician and producer (Atlanta, Georgia; Staunton, Virginia). \\ Trinton holds a Master of Arts degree in Composition and Music Theory from the University of Iowa. 
\end{center}
\endgroup

\end{document}